Solar wind predictions for the Parker Solar Probe orbit

### 2017-08-24 paperMVVB/sections/abstract.tex
referee version; vb edits summary + abstract; mvcolor

\date{First draft 9 August 2016; first changes 21 June 2017; second changes 17 July 2017; third changes 17 August 2017; received date; accepted date}

>>>>

\date{First draft 9 August 2016; first changes 21 June 2017; second changes 17 July 2017; third changes 17 August 2017; fourth changes 24 August 2017; received date; accepted date}
